Resilience and Home-Space for WSTS

### 2024-01-12 diapo/presentation.tex
up

$q_1(7) \to q_0(8) \to q_0(9) \to q_0(10) \to q_2(0) \to q_1(0)$

$q_1(6) \to q_1(5) \to q_1(4) \to q_1(3) \to q_1(2) \to q_1(1) \to q_1(0)$

@@

 \begin{definition}[\cite{BFM-ic17}]
The \emph{completion}   of a WBTS $\mathscr{S}=(S,\rightarrow, \leq)$ is the associated ordered transition system $\hat{\mathscr{S}}=(Ideals(S),\rightarrow, \subseteq)$ where 
%$Ideals(S)$ is the set of ideals of $S$ and
 $I \rightarrow J$ if $J$ belongs to the finite ideal decomposition of $\mathop{\downarrow} \post_{\mathscr{S}}(I)$. 
% The completion is always \emph{finitely branching} but it is not necessarly a WSTS since $\subseteq$ is not necessarly a wqo. 
%It is proved in  \cite{BFM-ic17} that $\hat{\mathscr{S}}$ is WSTS iff $\mathscr{S}=(S,\rightarrow, \leq)$ is $\omega^2$-WSTS. \\
\end{definition}

@@

  \end{frame}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{Resilience(s) for VASS}

  Remettre un déssin pour un VASS

>>>>

 \vspace{0.25cm}

 \only<2>{
$q_1(7) \to q_0(8) \to q_0(9) \to q_0(10) \to q_2(0) \to q_1(0)$
}

\only<1>{
$q_1(6) \to q_1(5) \to q_1(4) \to q_1(3) \to q_1(2) \to q_1(1) \to q_1(0)$
}

@@

 \begin{block}{Definition~\cite{BFM-ic17}}
The \emph{completion}   of a WBTS $\mathscr{S}=(S,\rightarrow, \leq)$ is the associated ordered transition system $\hat{\mathscr{S}}=(Ideals(S),\rightarrow, \subseteq)$ where 
%$Ideals(S)$ is the set of ideals of $S$ and
 $I \rightarrow J$ if $J$ belongs to the finite ideal decomposition of $\mathop{\downarrow} \post_{\mathscr{S}}(I)$. 
% The completion is always \emph{finitely branching} but it is not necessarly a WSTS since $\subseteq$ is not necessarly a wqo. 
%It is proved in  \cite{BFM-ic17} that $\hat{\mathscr{S}}$ is WSTS iff $\mathscr{S}=(S,\rightarrow, \leq)$ is $\omega^2$-WSTS. \\
\end{block}

@@

  \end{frame}
%vvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvvv
  \begin{frame}{Vector Addition System with States}

   \begin{center}
 	\begin{figure}
 	\vspace{.06cm}
\includegraphics[width=.4\textwidth]{FigC}
	\end{figure}
\end{center}
